Using DIT to simplify the DBF feasibility test

### 2013-07-18 dit-paper.tex
Removes trailing \newline

As was shown previously, the equations corresponding to job deadlines happening before $H$ are necessary and sufficient to test the feasibility, so only those can be considered. For constrained deadline systems, the end of the first busy period has been proven to be an acceptable upper limit for the DBF test as well, but this value depends on the $C_i$ and therefore cannot be used. In section \ref{sct:DIT}, a similar concept which does not depend on the value of $C_i$ is presented.

In \cite{lipariaverage}, the authors use the simplex algorithm to further reduce the number of equation to consider.\\

>>>>

As was shown previously, the equations corresponding to job deadlines happening before $H$ are necessary and sufficient to test the feasibility, so only those can be considered. For constrained deadline systems, the end of the first busy period has been proven to be an acceptable upper limit for the DBF test as well, but this value depends on the $C_i$ and therefore cannot be used. In section \ref{sct:DIT}, a similar concept which does not depend on the value of $C_i$ is presented.\\

In \cite{lipariaverage}, the authors use the simplex algorithm to further reduce the number of equation to consider.
